\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}
\usepackage{contour}
\usepackage[normalem]{ulem}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat {\section}{\bfseries \vspace{2pt} \raggedright \large}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-1pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-1pt}\item\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\\textit{#3} & {\color{dark-grey} \small #4}\\\end{tabular*}\vspace{-4pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}#1 & {\color{dark-grey}} \\\end{tabular*}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}
\color{text-grey}
\begin{document}
\begin{center}
    \textbf{\Huge Riwaz Udas} \\ \vspace{4pt}
    \scriptsize
    \faPhone* \ 0451337510 \ $|$ \
    \faEnvelope \ udasriwaz@gmail.com \ $|$ \
    \faLinkedin \ \href{https://www.linkedin.com/in/riwaz-udas-7aab521b1/}{riwaz-udas} \ $|$ \
    \faGithub \ \href{https://github.com/riwazudas}{GitHub} \ $|$ \
    \faGlobe \ \href{https://portfolio-website-496606.web.app}{Portfolio}
\end{center}

\section{PROFESSIONAL SUMMARY}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{Software Developer with a Master’s in Computer Science and a focus on AI-driven automation and scalable cloud architecture. Expert in C\#, Python, and Go, with a proven track record of designing asynchronous, message-based systems using Domain Driven Design (DDD) and CQRS patterns. Passionate about leveraging AI tools like Cursor and MCP to accelerate development cycles. Experienced in owning the full stack within cross-functional agile teams, deploying containerized applications to Azure/AWS, and building robust CI/CD pipelines to deliver customer-focused financial-grade solutions.}}
\end{itemize}

\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Programming:} C\#, Python, Go, Java, JavaScript, TypeScript, SQL \\
\textbf{Architectural Patterns:} CQRS, Domain Driven Design (DDD), Microservices, Asynchronous Message-based Systems \\
\textbf{Cloud \& DevOps:} Azure (Cloud Paradigms), AWS, Docker, Kubernetes (AKS/EKS), CI/CD (GitHub Actions/Jenkins) \\
\textbf{AI \& Automation:} Cursor, Context Engineering, MCP Integration, RAG, LangChain, Hugging Face, LLM Fine-tuning \\
\textbf{Backend \& Web:} FastAPI, Spring Boot, REST API Design, OAuth 2.0, PostgreSQL, VectorDB, Redis
}}
\end{itemize}

\section{EXPERIENCE}
\resumeSubHeadingListStart
\resumeSubheading{Byju’s}{Oct 2023 -- Jan 2024}{Member of Technical Staff I}{Bangalore, India}
\resumeItemListStart
\resumeItem{Engineered a high-throughput authentication platform using \textbf{CQRS patterns}, decoupling command and query operations to improve system responsiveness for 2M+ daily users.}
\resumeItem{Automated CI/CD workflows using \textbf{Docker and AWS EKS}, reducing deployment lead time by 40\% and ensuring zero-downtime releases for critical identity services.}
\resumeItem{Implemented \textbf{asynchronous message-based communication} between microservices, enhancing system resilience and fault tolerance during peak traffic spikes.}
\resumeItem{Optimized \textbf{C\# and Go-based backend services} by refactoring legacy code into modular, domain-driven components, directly reducing API latency by 25\%.}
\resumeItem{Provided Level 3 operational support, diagnosing complex production incidents and implementing automated monitoring alerts via Prometheus/Grafana.}
\resumeItemListEnd

\resumeSubheading{Byju’s}{Jan 2023 -- Sep 2023}{Software Engineering Intern}{Bangalore, India}
\resumeItemListStart
\resumeItem{Collaborated in an \textbf{Agile cross-functional team} to build and maintain scalable REST APIs, ensuring 99.9\% uptime for core product verticals.}
\resumeItem{Integrated \textbf{automated testing suites} (200+ tests), significantly reducing regression bugs and improving code quality in the authentication module.}
\resumeItem{Developed custom monitoring metrics to track system health, providing actionable insights that reduced incident resolution time by 30\%.}
\resumeItem{Worked closely with senior architects to implement \textbf{Domain Driven Design} principles, ensuring the codebase remained maintainable and scalable.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{PROJECTS}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered CareerPilot Application}}{}
\resumeItemListStart
\resumeItem{Built a full-stack platform using \textbf{React and Node.js} that integrates the \textbf{Gemini API} to automate resume tailoring using psychological framing strategies.}
\resumeItem{Engineered a custom LaTeX compilation engine that dynamically generates ATS-optimized PDFs, demonstrating advanced backend automation capabilities.}
\resumeItem{Implemented a responsive glassmorphism UI, focusing on user experience and accessibility for job seekers.}
\resumeItem{Deployed on cloud infrastructure with automated CI/CD pipelines, ensuring rapid iteration and feature deployment.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Nepal Law AI Platform using Multilingual RAG}}{}
\resumeItemListStart
\resumeItem{Developed a \textbf{Retrieval-Augmented Generation (RAG)} system for legal queries, utilizing vector search and contextual reranking to provide accurate, domain-specific responses.}
\resumeItem{Designed \textbf{self-healing data pipelines} that automatically ingest and chunk legal documents, maintaining a consistent and up-to-date knowledge base.}
\resumeItem{Built scalable \textbf{FastAPI backend services} deployed on GCP, showcasing expertise in building AI-integrated production applications.}
\resumeItem{Applied multilingual embeddings to support cross-language semantic retrieval, significantly improving search accuracy for legal professionals.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Social Media Geotagging using LLMs (Master’s Thesis)}}{}
\resumeItemListStart
\resumeItem{Fine-tuned \textbf{LLaMA and Mistral models} using \textbf{PyTorch and Hugging Face}, achieving state-of-the-art accuracy in hierarchical geospatial prediction.}
\resumeItem{Implemented \textbf{LoRA and PEFT techniques} to optimize model performance on multi-million record datasets, demonstrating efficient resource utilization.}
\resumeItem{Architected a multi-task learning framework that predicts geographic levels (suburb to state), showcasing advanced AI system design.}
\resumeItem{Utilized \textbf{distributed GPU training} and MLOps tools (Weights \& Biases) to manage complex model evaluation and training lifecycles.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading{University of Melbourne}{2024 -- 2025}{Master of Computer Science}{Melbourne, Australia}
\resumeSubheading{Vellore Institute of Technology}{2019 -- 2023}{Bachelor of Technology, Computer Science}{India}
\resumeSubHeadingListEnd

\section{CERTIFICATIONS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{\textbf{Salesforce Certified AI Associate} $|$ \textbf{Algorithmic Thinking} -- Rice University $|$ \textbf{AI Foundation} -- NASSCOM $|$ \textbf{Big Data Foundation} -- NASSCOM}}
\end{itemize}
\end{document}