\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\usepackage{contour}
\usepackage[normalem]{ulem}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-1pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}#1 & {\color{dark-grey}} \\ \end{tabular*}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

\begin{document}

\begin{center}
    \textbf{\Huge Riwaz Udas} \\ \vspace{4pt}
    \scriptsize
    \faPhone* \ 0451337510 \ $|$ \
    \faEnvelope \ udasriwaz@gmail.com \ $|$ \
    \faLinkedin \ \href{https://www.linkedin.com/in/riwaz-udas-7aab521b1/}{riwaz-udas} \ $|$ \
    \faGithub \ \href{https://github.com/riwazudas}{GitHub} \ $|$ \
    \faGlobe \ \href{https://portfolio-website-496606.web.app}{Portfolio}
\end{center}

\section{PROFESSIONAL SUMMARY}
\small{AI-Native Full Stack Developer with a Master’s in Computer Science and a proven track record in building scalable, production-grade systems. Expert in integrating LLM APIs (OpenAI, Anthropic, Gemini) into business workflows and architecting modern eCommerce and internal tool solutions. Passionate about AI-assisted development, cloud-native infrastructure (AWS/Azure), and modernizing legacy operations. Committed to high-ownership, rapid-delivery environments.}

\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{AI-Native Development:} LLM APIs (OpenAI, Anthropic, Gemini), RAG, LangChain, LlamaIndex, Prompt Engineering, Agentic Workflows, Cursor/Claude Code. \\
\textbf{Full Stack Development:} Python (FastAPI), Go, JavaScript/TypeScript, React, Next.js, REST API Design, Microservices. \\
\textbf{Cloud \& Infrastructure:} AWS, GCP, Azure (transferable), Docker, Kubernetes, CI/CD, Linux, System Observability (Prometheus/Grafana). \\
\textbf{Data \& ERP Integration:} PostgreSQL, MongoDB, VectorDB, SQL Optimization, ERP/API Integration, OAuth 2.0.
}}
\end{itemize}

\section{EXPERIENCE}
\resumeSubHeadingListStart
\resumeSubheading{Byju’s}{Oct 2023 -- Jan 2024}{Member of Technical Staff I}{Bangalore, India}
\resumeItemListStart
\resumeItem{Spearheaded the development of a high-scale OAuth 2.0 identity platform using Ory Hydra, securing authentication for millions of active users.}
\resumeItem{Engineered 30+ production REST APIs, reducing latency by 20\% through optimized SQL indexing and query refactoring for 2M+ daily users.}
\resumeItem{Implemented advanced rate-limiting middleware and behavioral analysis, successfully blocking 50K+ malicious DDoS requests and enhancing system security.}
\resumeItem{Automated lifecycle management for 100M+ OAuth records using Golang, significantly reducing manual operational overhead and database storage costs.}
\resumeItem{Collaborated with cross-functional teams to integrate third-party mobile OTP services, improving login success rates by 15\% through robust error handling.}
\resumeItemListEnd

\resumeSubheading{Byju’s}{Jan 2023 -- Sep 2023}{Software Engineering Intern}{Bangalore, India}
\resumeItemListStart
\resumeItem{Developed and deployed scalable backend microservices in Go, supporting 10+ product verticals within an enterprise environment.}
\resumeItem{Integrated Prometheus and Grafana for real-time observability, configuring 15+ automated alerts that reduced mean-time-to-resolution (MTTR) for production incidents.}
\resumeItem{Authored 200+ unit and integration tests, ensuring 95\% code coverage for critical authentication and identity management workflows.}
\resumeItem{Participated in Agile sprints, contributing to the migration of legacy services into a modular, interface-based architecture.}
\resumeItemListEnd

\resumeSubheading{Quantum AI Cloud}{Jul 2024 -- Sep 2024}{Research Intern}{Melbourne, Australia}
\resumeItemListStart
\resumeItem{Developed reinforcement learning frameworks (PPO, SAC, IMPALA) for intelligent workload scheduling in hybrid classical-quantum cloud environments.}
\resumeItem{Simulated distributed task placement scenarios, providing data-driven insights for optimizing resource allocation in cloud-native infrastructure.}
\resumeItem{Collaborated with senior researchers to evaluate AI-driven orchestration strategies, bridging the gap between theoretical AI models and practical cloud deployment.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{PROJECTS}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered CareerPilot Application}}{}
\resumeItemListStart
\resumeItem{Built an AI-native career platform using React, Node.js, and the Google Gemini API to automate professional resume tailoring.}
\resumeItem{Engineered a custom backend for real-time LaTeX compilation, enabling dynamic PDF generation with integrated psychological framing strategies.}
\resumeItem{Implemented a responsive glassmorphism UI with live markdown rendering, significantly improving user engagement and editing efficiency.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Nepal Law AI Platform using Multilingual RAG}}{}
\resumeItemListStart
\resumeItem{Developed a multilingual legal AI platform using RAG pipelines to provide accurate, context-aware answers for complex legal queries.}
\resumeItem{Implemented cross-language semantic retrieval using vector search and contextual reranking, supporting both English and Nepali documents.}
\resumeItem{Automated data ingestion and embedding pipelines, creating a self-healing knowledge base that maintains consistency over time.}
\resumeItem{Deployed on GCP using FastAPI, demonstrating ability to manage end-to-end AI-native product lifecycles.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Social Media Geotagging using LLMs (Master’s Thesis)}}{}
\resumeItemListStart
\resumeItem{Fine-tuned LLaMA, Gemma, and Mistral models using LoRA and PEFT to predict hierarchical geographic structures from social media data.}
\resumeItem{Processed multi-million record datasets using PyTorch and Hugging Face Accelerate, achieving state-of-the-art accuracy in multimodal fusion.}
\resumeItem{Designed a multi-task learning architecture that successfully predicted suburb, city, and state-level locations.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading{University of Melbourne}{2024 -- 2025}{Master of Computer Science}{Melbourne, Australia}
\resumeSubheading{Vellore Institute of Technology}{2019 -- 2023}{Bachelor of Technology, Computer Science}{India}
\resumeSubHeadingListEnd

\section{CERTIFICATIONS}
\small{Salesforce Certified AI Associate $|$ Algorithmic Thinking (Rice University) $|$ AI Foundation (NASSCOM) $|$ Big Data Foundation (NASSCOM) $|$ Kotlin for Java Developers (JetBrains)}

\end{document}