\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{a}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\usepackage{contour}
\usepackage[normalem]{ulem}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-1pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}#1 & {\color{dark-grey}} \\ \end{tabular*}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

\begin{document}

\begin{center}
    \textbf{\Huge Riwaz Udas} \\ \vspace{4pt}
    \scriptsize
    \faPhone* \ 0451337510 \ $|$ \
    \faEnvelope \ udasriwaz@gmail.com \ $|$ \
    \faLinkedin \ \href{https://www.linkedin.com/in/riwaz-udas-7aab521b1/}{riwaz-udas} \ $|$ \
    \faGithub \ \href{https://github.com/riwazudas}{GitHub} \ $|$ \
    \faGlobe \ \href{https://portfolio-website-496606.web.app}{Portfolio}
\end{center}

\section{PROFESSIONAL SUMMARY}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{Software Engineer with a strong foundation in functional programming paradigms and scalable backend architecture. Expert in building high-availability systems using Go, Python, and PostgreSQL, with a deep focus on observability (Prometheus/Grafana) and CI/CD automation. Proven track record of optimizing production systems for millions of users and a passion for technical craft, clean code, and sustainable engineering practices. Eager to leverage experience in distributed systems and API design to contribute to the Elixir/Phoenix ecosystem at SuperAPI.}}
\end{itemize}

\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Languages:} Go, Python, Java, JavaScript, SQL, C, C\# \\
\textbf{Backend \& Frameworks:} REST API Design, Microservices, OAuth 2.0, FastAPI, Spring Boot, Node.js \\
\textbf{Databases:} PostgreSQL (Query Optimization, Indexing), MongoDB, VectorDB \\
\textbf{Cloud \& DevOps:} AWS (ECS/EKS), Terraform, Docker, Kubernetes, GitHub Actions, CI/CD \\
\textbf{Observability:} Grafana, Prometheus, Alerting Systems, Logging Pipelines \\
\textbf{AI/ML Engineering:} RAG, Hugging Face, PyTorch, LLM Fine-tuning, Vector Search
}}
\end{itemize}

\section{EXPERIENCE}
\resumeSubHeadingListStart
\resumeSubheading{Byju’s}{Oct 2023 -- Jan 2024}{Member of Technical Staff I}{Bangalore, India}
\resumeItemListStart
\resumeItem{Engineered a high-scale OAuth 2.0 identity platform using Ory Hydra, supporting secure authentication for \textbf{2M+ daily active users}.}
\resumeItem{Optimized PostgreSQL query performance and indexing strategies, reducing API response latency by \textbf{30\%} for core identity services.}
\resumeItem{Implemented sliding-window rate limiting middleware with IP filtering, successfully mitigating DDoS attempts and blocking \textbf{50K+ malicious requests}.}
\resumeItem{Built comprehensive observability dashboards using \textbf{Prometheus and Grafana}, enabling proactive incident response and reducing MTTR (Mean Time To Recovery) by 40\%.}
\resumeItem{Automated CI/CD pipelines using GitHub Actions to streamline deployment to AWS ECS/EKS, ensuring zero-downtime releases for critical microservices.}
\resumeItemListEnd

\resumeSubheading{Byju’s}{Jan 2023 -- Sep 2023}{Software Engineering Intern}{Bangalore, India}
\resumeItemListStart
\resumeItem{Developed modular REST APIs in Go, adhering to clean architecture principles to improve code maintainability and test coverage.}
\resumeItem{Integrated custom Prometheus metrics across 30+ microservices to track request latency, authentication failures, and system throughput.}
\resumeItem{Collaborated with an 8-person platform engineering team to refactor legacy services into an interface-based architecture, increasing testability.}
\resumeItem{Authored 200+ automated unit and integration tests, ensuring high reliability for mission-critical authentication workflows.}
\resumeItemListEnd

\resumeSubheading{Quantum AI Cloud}{Jul 2024 -- Sep 2024}{Research Intern}{Melbourne, Australia}
\resumeItemListStart
\resumeItem{Designed reinforcement learning frameworks for intelligent task scheduling in distributed cloud environments, optimizing resource allocation.}
\resumeItem{Implemented and benchmarked advanced RL algorithms (PPO, SAC, IMPALA) to improve workload orchestration efficiency.}
\resumeItem{Collaborated with senior researchers to evaluate AI-driven orchestration strategies for hybrid classical-quantum infrastructure.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{PROJECTS}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Nepal Law AI Platform (Multilingual RAG)}}{ }
\resumeItemListStart
\resumeItem{Built a scalable RAG pipeline for legal queries using FastAPI, vector search, and contextual reranking for English/Nepali documents.}
\resumeItem{Designed self-healing knowledge base workflows to maintain retrieval consistency, ensuring high accuracy for complex legal queries.}
\resumeItem{Deployed infrastructure on GCP with automated ingestion pipelines, demonstrating end-to-end cloud-native development skills.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{AI Portfolio Website with Personal RAG Chatbot}}{ }
\resumeItemListStart
\resumeItem{Developed a full-stack AI portfolio featuring a RAG-based chatbot trained on personal project data and technical documentation.}
\resumeItem{Implemented semantic search pipelines using vector embeddings to enable conversational querying over portfolio content.}
\resumeItem{Deployed using Firebase Hosting with FastAPI backend inference services, ensuring low-latency performance.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Social Media Geotagging (Master’s Thesis)}}{ }
\resumeItemListStart
\resumeItem{Fine-tuned LLaMA and Mistral models using PyTorch and Hugging Face, processing multi-million record datasets for geospatial prediction.}
\resumeItem{Applied LoRA and instruction tuning to optimize model performance, achieving high accuracy in hierarchical multi-task learning.}
\resumeItem{Utilized distributed GPU training and Hugging Face Accelerate to manage large-scale model training workflows.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading{University of Melbourne}{Feb 2024 -- Dec 2025}{Master of Computer Science}{Melbourne, Australia}
\resumeSubheading{Vellore Institute of Technology}{2019 -- 2023}{Bachelor of Technology, Computer Science}{India}
\resumeSubHeadingListEnd

\section{CERTIFICATIONS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{Salesforce Certified AI Associate $|$ Algorithmic Thinking (Rice University) $|$ AI Foundation (NASSCOM) $|$ Big Data Foundation (NASSCOM) $|$ Kotlin for Java Developers (JetBrains)}}
\end{itemize}
\end{document}