\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}
\usepackage{contour}
\usepackage[normalem]{ulem}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat {\section}{\bfseries \vspace{2pt} \raggedright \large}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-1pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-1pt}\item\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\\textit{#3} & {\color{dark-grey} \small #4}\\\end{tabular*}\vspace{-4pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}#1 & {\color{dark-grey}} \\\end{tabular*}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}
\color{text-grey}
\begin{document}
\begin{center}
    \textbf{\Huge Riwaz Udas} \\ \vspace{4pt}
    \scriptsize
    \faPhone* \ 0451337510 \ $|$ \
    \faEnvelope \ udasriwaz@gmail.com \ $|$ \
    \faLinkedin \ \href{https://www.linkedin.com/in/riwaz-udas-7aab521b1/}{riwaz-udas} \ $|$ \
    \faGithub \ \href{https://github.com/riwazudas}{GitHub} \ $|$ \
    \faGlobe \ \href{https://portfolio-website-496606.web.app}{Portfolio}
\end{center}

\section{PROFESSIONAL SUMMARY}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
Backend Engineer with a strong foundation in functional programming paradigms and distributed systems. Expert in building high-concurrency, fault-tolerant microservices with a focus on Elixir/Erlang-style concurrency models. Proven track record in scaling authentication platforms for 2M+ daily users, implementing robust rate-limiting, and optimizing SQL/NoSQL performance. Seeking to leverage deep expertise in API design and distributed architecture to contribute to SuperAPI PTY LTD’s mission in Melbourne.
}}
\end{itemize}

\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Functional \& Backend:} Elixir (Erlang/OTP concepts), Go, Python, FastAPI, Microservices, REST API Design \\
\textbf{Systems \& Concurrency:} Distributed Systems, OAuth 2.0, Rate Limiting, DDoS Mitigation, Message Queues (Kafka) \\
\textbf{Databases:} PostgreSQL, MySQL, MongoDB, VectorDB, Query Optimization, Indexing \\
\textbf{Cloud \& DevOps:} AWS (ECS/EKS), GCP, Docker, Kubernetes, CI/CD, Prometheus, Grafana \\
\textbf{AI \& Data:} PyTorch, Hugging Face, RAG, LLM Fine-tuning, Vector Search, Multilingual AI
}}
\end{itemize}

\section{EXPERIENCE}
\resumeSubHeadingListStart
\resumeSubheading{Byju’s}{Oct 2023 -- Jan 2024}{Member of Technical Staff I}{Bangalore, India}
\resumeItemListStart
\resumeItem{Engineered a high-concurrency \textbf{OAuth 2.0 identity platform} using Ory Hydra, ensuring 99.99\% uptime for authentication services serving \textbf{2M+ daily active users}.}
\resumeItem{Architected \textbf{30+ production REST APIs} with a focus on low-latency response times, utilizing interface-based modular design to improve code maintainability by 40\%.}
\resumeItem{Implemented a \textbf{sliding-window rate limiting middleware} that successfully mitigated DDoS attacks, blocking \textbf{50K+ malicious requests} per day and protecting downstream services.}
\resumeItem{Optimized \textbf{PostgreSQL indexing strategies} and query execution plans, resulting in a \textbf{30\% reduction in API latency} for identity-heavy operations.}
\resumeItem{Led Level 3 operational support, diagnosing and resolving complex cross-service production incidents in a distributed microservices environment.}
\resumeItemListEnd

\resumeSubheading{Byju’s}{Jan 2023 -- Sep 2023}{Software Engineering Intern}{Bangalore, India}
\resumeItemListStart
\resumeItem{Developed core components of a \textbf{Golang-based authentication service}, implementing token validation and OTP workflows across 10+ product verticals.}
\resumeItem{Integrated \textbf{Prometheus and Grafana} to build a comprehensive observability suite, tracking request latency and authentication failure rates in real-time.}
\resumeItem{Collaborated with an 8-person platform team to refactor legacy authentication modules, improving system reliability and reducing technical debt.}
\resumeItem{Automated lifecycle management for \textbf{100M+ OAuth records} annually, significantly reducing database storage costs and improving query performance.}
\resumeItemListEnd

\resumeSubheading{Quantum AI Cloud}{Jul 2024 -- Sep 2024}{Research Intern}{Melbourne, Australia}
\resumeItemListStart
\resumeItem{Designed reinforcement learning frameworks for \textbf{intelligent task scheduling} in distributed cloud environments, optimizing resource allocation.}
\resumeItem{Implemented advanced RL algorithms (PPO, SAC, IMPALA) to manage dynamic workloads, demonstrating a 15\% improvement in scheduling efficiency.}
\resumeItem{Collaborated with senior researchers to evaluate AI-driven orchestration strategies for hybrid classical-quantum infrastructure.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{PROJECTS}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Nepal Law AI Platform (Multilingual RAG)}}{ }
\resumeItemListStart
\resumeItem{Built a scalable \textbf{RAG pipeline} for legal document retrieval using FastAPI and vector search, enabling semantic querying across English and Nepali.}
\resumeItem{Developed automated ingestion and chunking pipelines that process thousands of legal documents, maintaining retrieval consistency via self-healing workflows.}
\resumeItem{Deployed the entire infrastructure on \textbf{GCP}, utilizing containerized microservices for high availability.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Social Media Geotagging (Master’s Thesis)}}{ }
\resumeItemListStart
\resumeItem{Fine-tuned \textbf{LLaMA and Mistral} models using PyTorch, applying LoRA and multimodal fusion to predict geographic locations from social media metadata.}
\resumeItem{Managed distributed GPU training on multi-million record datasets using \textbf{Hugging Face Accelerate}, optimizing training throughput by 2x.}
\resumeItem{Authored a hierarchical multi-task learning architecture that achieved state-of-the-art accuracy in suburb-level geolocation.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{AI Portfolio with Personal RAG Chatbot}}{ }
\resumeItemListStart
\resumeItem{Engineered an AI-powered chatbot that provides conversational access to technical project data using vector embeddings.}
\resumeItem{Built a robust \textbf{FastAPI backend} with asynchronous inference capabilities, deployed via Firebase for global accessibility.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading{University of Melbourne}{Feb 2024 -- Dec 2025}{Master of Computer Science}{Melbourne, Australia}
\resumeSubheading{Vellore Institute of Technology}{2019 -- 2023}{Bachelor of Technology, Computer Science}{India}
\resumeSubHeadingListEnd

\section{CERTIFICATIONS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{\textbf{Salesforce Certified AI Associate} $|$ \textbf{Algorithmic Thinking} -- Rice University $|$ \textbf{Artificial Intelligence Foundation} -- NASSCOM}}
\end{itemize}
\end{document}